Benchmarks of the Non-Relativistic Hydrodynamics Algorithms in \thornado

### 2017-02-10 Documents/Euler/Benchmarks1D/draft.tex
edited captions and increased image size

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=.78\textwidth]{den128comp_20}
  \end{center}
  \caption{Results showing the density for Sod's shock tube at $t=0.2$, computed with 128 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den128comp}
\end{figure}
%\newpage

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel128comp_20} &
	  \includegraphics[width=.425\textwidth]{prs128comp_20}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den128comp}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\subsection{Test 2}
For subsequent tests, the number of cells was consistent within each test, and the integration method was varied as in the first test. 
The graphs for the second test show a result common throughout many of the different tests: The first order integration method is considerably far from the exact solution; the second and third order integration methods yield nearly identical results which are near, but not exactly equal to, the exact solution. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T2.png}	
  \end{center}
  \caption{Results showing the density for test 2 at $t=0.2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T2}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T2.png} &
	  \includegraphics[width=.425\textwidth]{prs_T2.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T2}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\subsection{Test 3}
Test 3 shows results similar to Test 2. The deviation of experimental results from exact is especially noticeable in velocity. Near the initial point of discontinuity, the exact results appear completely horizontal. Method 1 almost completely ignores this horizontal part, while Methods 2 and 3 smooth it out considerably. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T3.png}	
  \end{center}
  \caption{Results showing the density for test 3 at $t=0.15$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T3}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T3.png} &
	  \includegraphics[width=.425\textwidth]{prs_T3.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T3}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T4.png}	
  \end{center}
  \caption{Results showing the density for the Noh problem at $t=1$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T4}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T4.png} &
	  \includegraphics[width=.425\textwidth]{prs_T4.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T4}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T5.png}	
  \end{center}
  \caption{Results showing the density for test 5 at $t=0.012$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T5}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T5.png} &
	  \includegraphics[width=.425\textwidth]{prs_T5.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T5}:
  velocity (left panel) and pressure (right panel).}
\end{figure}
\clearpage

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T6.png}	
  \end{center}
  \caption{Results showing the density for test 6 at $t=0.035$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T6}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T6.png} &
	  \includegraphics[width=.425\textwidth]{prs_T6.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T6}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T7.png}	
  \end{center}
  \caption{Results showing the density for test 7 at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T7}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T7.png} &
	  \includegraphics[width=.425\textwidth]{prs_T7.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T7}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T8.png}	
  \end{center}
  \caption{Results showing the density for test 8 at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T8}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{vel_T8.png} &
	  \includegraphics[width=.425\textwidth]{prs_T8.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T8}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T12_400.png}	
  \end{center}
  \caption{Results showing the density for the Woodward-Collela blast wave problem at $t=1$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
  \label{fig:den_T12_400}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{den_T12_2000.png}	
  \end{center}
  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_400} computed with 2000 cells}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{vel_T12_400.png}	
  \end{center}
  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_400}}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{vel_T12_2000.png}	
  \end{center}
  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_400} computed with 2000 cells}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{prs_T12_400.png}	
  \end{center}
  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_400}}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{prs_T12_2000.png}	
  \end{center}
  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_400} computed with 2000 cells}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.78\textwidth]{1000.png}	
  \end{center}
  \caption{density, 1000 cells}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{10.png} &
	  \includegraphics[width=.425\textwidth]{10zoom.png}
	\end{tabular}
  \end{center}
  \caption{density, beta=10}
  \label{fig:pvcellcomp}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{50.png} &
	  \includegraphics[width=.425\textwidth]{50zoom.png}
	\end{tabular}
  \end{center}
  \caption{density, beta=50}
  \label{fig:pvcellcomp}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.425\textwidth]{300.png} &
	  \includegraphics[width=.425\textwidth]{300zoom.png}
	\end{tabular}
  \end{center}
  \caption{density, beta=300}
  \label{fig:pvcellcomp}
\end{figure}

>>>>

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=.95\textwidth]{den128comp_20}
  \end{center}
  \caption{Results showing the density for Sod's shock tube at $t=0.2$, computed with 128 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den128comp}
\end{figure}
%\newpage

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel128comp_20} &
	  \includegraphics[width=.475\textwidth]{prs128comp_20}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den128comp}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\subsection{Test 2}
For subsequent tests, the number of cells was consistent within each test, and the integration method was varied as in the first test. 
The graphs for the second test show a result common throughout many of the different tests: The first order integration method is considerably far from the exact solution; the second and third order integration methods yield nearly identical results which are near, but not exactly equal to, the exact solution. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T2.png}	
  \end{center}
  \caption{Results showing the density for test 2 at $t=0.2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T2}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T2.png} &
	  \includegraphics[width=.475\textwidth]{prs_T2.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T2}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\subsection{Test 3}
Test 3 shows results similar to Test 2. The deviation of experimental results from exact is especially noticeable in velocity. Near the initial point of discontinuity, the exact results appear completely horizontal. Method 1 almost completely ignores this horizontal part, while Methods 2 and 3 smooth it out considerably. 
\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T3.png}	
  \end{center}
  \caption{Results showing the density for test 3 at $t=0.15$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T3}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T3.png} &
	  \includegraphics[width=.475\textwidth]{prs_T3.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T3}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T4.png}	
  \end{center}
  \caption{Results showing the density for the Noh problem at $t=1$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T4}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T4.png} &
	  \includegraphics[width=.475\textwidth]{prs_T4.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T4}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T5.png}	
  \end{center}
  \caption{Results showing the density for test 5 at $t=0.012$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T5}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T5.png} &
	  \includegraphics[width=.475\textwidth]{prs_T5.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T5}:
  velocity (left panel) and pressure (right panel).}
\end{figure}
\clearpage

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T6.png}	
  \end{center}
  \caption{Results showing the density for test 6 at $t=0.035$, computed with 200 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T6}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T6.png} &
	  \includegraphics[width=.475\textwidth]{prs_T6.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T6}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T7.png}	
  \end{center}
  \caption{Results showing the density for test 7 at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T7}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T7.png} &
	  \includegraphics[width=.475\textwidth]{prs_T7.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T7}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T8.png}	
  \end{center}
  \caption{Results showing the density for test 8 at $t=2$, computed with 100 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The exact solution, obtained with Toro's Riemann solver, is given by the dash-dotted pink line.}
  \label{fig:den_T8}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{vel_T8.png} &
	  \includegraphics[width=.475\textwidth]{prs_T8.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:den_T8}:
  velocity (left panel) and pressure (right panel).}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T12_400.png}	
  \end{center}
  \caption{Results showing the density for the Woodward-Collela blast wave problem at $t=0.038$, computed with 400 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue). The solution labelled ``exact' and given by the dash-dotted pink line is the results of the problem when computed using the third-order integration method with 2000 cells.}
  \label{fig:den_T12_400}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{den_T12_2000.png}	
  \end{center}
  \caption{Results for the density from the same experiments as shown in Figure~\ref{fig:den_T12_400}~computed with 2000 cells}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{vel_T12_400.png}	
  \end{center}
  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_400}}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{vel_T12_2000.png}	
  \end{center}
  \caption{Results for the velocity from the same experiments as shown in Figure~\ref{fig:den_T12_400}~computed with 2000 cells}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{prs_T12_400.png}	
  \end{center}
  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_400}}
\end{figure}

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{prs_T12_2000.png}	
  \end{center}
  \caption{Results for the pressure from the same experiments as shown in Figure~\ref{fig:den_T12_400}~computed with 2000 cells}
\end{figure}

@@

\begin{figure}[h]
  \begin{center}
     \includegraphics[width=.95\textwidth]{1000.png}	
  \end{center}
  \caption{Results showing the density for the Shock Entropy Wave problem at $t=1.8$, computed with 1000 cells with methods of different orders: 1st (solid red), 2nd (dashed green) and 3rd (dotted blue).}
  \label{fig:shock}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{10.png} &
	  \includegraphics[width=.475\textwidth]{10zoom.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:shock}~at two different zoom levels, computed with 200 cells and beta set to 10. The solution labelled ``exact' and given by the dotted blue line is the results of the problem when computed using the third-order integration method with 2000 cells.}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{50.png} &
	  \includegraphics[width=.475\textwidth]{50zoom.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:shock}~at two different zoom levels, computed with 200 cells and beta set to 50.}
\end{figure}

\begin{figure}
  \begin{center}
	\begin{tabular}{cc}
      \includegraphics[width=.475\textwidth]{300.png} &
	  \includegraphics[width=.475\textwidth]{300zoom.png}
	\end{tabular}
  \end{center}
  \caption{Results from the same experiments as shown in Figure~\ref{fig:shock}~at two different zoom levels, computed with 200 cells and beta set to 300.}
\end{figure}
